---
title: "LMER Muse longitudinal analyses"
author: "Eugenie Roudaia"
date: "March 17, 2019"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lme4)
library(lmerTest)
library(pbkrtest)
#library(devtools)
#install.packages("digest")
#devtools::install_github('bcjaeger/r2glmm')
#library(r2glmm)
library(dplyr)
library(ggplot2)
```

```{r load data}
load("~/github/muse_longitudinal/lmers/fooof_wMeta_ch1ch4_long_fixed.RData", verbose = TRUE)
```

## looking at fooof parameters

```{r}
ggplot(fooof_ch1_hasAlpha, aes(x = age, y = err))+
  geom_point()

ggplot(fooof_ch1_hasAlpha, aes(x = age, y = r2))+
  geom_point()


quantile(fooof_ch1_hasAlpha$err, c(0.05, 0.95))

```
### Will be excluding all estimates that have an error > 0.2 and r2 < 0.7 (totally random cutoffs.. need better ones 

### Check to see how many estimates each session has. 

```{r}

cnts =fooof_ch1_hasAlpha %>%
  group_by(session_id, type, user_id, gender, age, age_group, sessOrder)%>%
  summarise(n_int = length(bg_int), 
            n_slope = length(bg_slope),
            n_pk_freq = length(pk_freq))


cnts =fooof_ch4_hasAlpha %>%
  group_by(session_id, type, user_id, gender, age, age_group, sessOrder)%>%
  summarise(n_int = length(bg_int), 
            n_slope = length(bg_slope),
            n_pk_freq = length(pk_freq))


summary(cnts)
```

i.e. we have multiple estimates per session (probably more than one epoch analyzed)

### Look at both channels after removing bad fits
```{r}

fooof_ch4_hasAlpha$channel = 'Right'
fooof_ch1_hasAlpha$channel = 'Left'
fooof_ch14_hasAlpha = rbind(fooof_ch1_hasAlpha, fooof_ch4_hasAlpha)
unique(fooof_ch14_hasAlpha$channel)

OKfits = fooof_ch14_hasAlpha%>%
  dplyr::filter(r2>0.8 & err<0.15)

ggplot(OKfits, aes(x = age, y = r2))+
  geom_point()

ggplot(OKfits, aes(x = age, y = err))+
  geom_point()

ggplot(OKfits, aes(x = age_group , y = bg_int, col = channel))+
  geom_boxplot(position = position_dodge(width = 0.3))

ggplot(OKfits, aes(x = age_group , y = bg_slope, col = channel))+
  geom_boxplot(position = position_dodge(width = 0.3))

ggplot(OKfits, aes(x = age_group , y = pk_freq, col = channel))+
  geom_boxplot(position = position_dodge(width = 0.3))

ggplot(OKfits, aes(x = age_group , y = pk_amp, col = channel))+
  geom_boxplot(position = position_dodge(width = 0.3))

```

Will analyze channels separately.. 

# FOOOF lmer setup

fooof_ch1_hasAlpha: 
"session_id"          "bg_int"              "bg_slope"            "pk_freq"            
 [5] "pk_amp"              "pk_bw"               "r2"                  "err"                
 [9] "type"                "channel"             "X"                   "user_id"            
[13] "session_timestamp"   "completed_seconds"   "year_of_birth"       "gender"             
[17] "handedness"          "total_session_count" "total_musing_time"   "bird_count"         
[21] "recovery_count"      "seconds_calm"        "active_days"         "avg_sess_per_month" 
[25] "age"                 "age_group"           "sessOrder"           "sessDate"           
[29] "sessDaysSince1st"    "sessDaySincePrev"   

## centre my variables and do contr.sum coding
```{r}
options(contrasts = c("contr.sum", "contr.poly"))

# center sessOrder on session 15
OKfits_c = OKfits%>%
  mutate(sessOrder = sessOrder - 12)
OKfits_c$handedness =  factor(OKfits_c$handedness, levels = c("left", "mostly_left", "ambidextrous", "none", "mostly_right", "right"))


```

# by-user intercept LMERs, meditation only. 
with by-user intercepts and main effects of age, gender, sessOrder,  
their two-way interactions, and three-way with sessOrder:age:gender


## med, each channel - Bg Intercept
```{r, echo = TRUE}

int_i = lmer(bg_int ~ age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Left"))
#summary(int_i)
anova(int_i)

int_i = lmer(bg_int ~ age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Right"))
#summary(int_i)
anova(int_i)
```

# med, each channel - Bg Slope
```{r}
bg_slope_i = lmer(bg_slope ~age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Left"))
anova(bg_slope_i)
#summary(bg_slope_i)


bg_slope_i = lmer(bg_slope ~age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Right"))
anova(bg_slope_i)
#summary(bg_slope_i)

```

# med, each channel - Peak Freq
```{r}
pk_freq_i = lmer(pk_freq ~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Left"))
anova(pk_freq_i)
#summary(pk_freq_i)

pk_freq_i = lmer(pk_freq ~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Right"))
anova(pk_freq_i)
#summary(pk_freq_i)
```


# med, each channel - Peak Ampli
```{r}

pk_amp_i = lmer(pk_amp ~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Left"))
anova(pk_amp_i)
pk_amp_i = lmer(pk_amp ~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                 +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Right"))
anova(pk_amp_i)
#summary(pk_amp_i)



```

# med, each channel - Peak BWD
```{r}
pk_bw_i = lmer(pk_bw~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Left"))
anova(pk_bw_i)
pk_bw_i = lmer(pk_bw~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), data = subset(OKfits_c, type == "med" & channel == "Right"))
anova(pk_bw_i)
#summary(pk_bw_i)

```

# LMER for band power and PAA/PAF in ch1
## loading data and setup
```{r setting up data frame}
load("~/github/muse_longitudinal/Muse classic bands/psd_freqBandAve_all.Rdata")

names(bnds_psd_ch1)

bnds_psd_ch1 = bnds_psd_ch1%>%
  mutate(sessOrder = sessOrder - 12)
bnds_psd_ch4 = bnds_psd_ch4%>%
  mutate(sessOrder = sessOrder - 12)

bnds_psd_ch1$handedness =  factor(bnds_psd_ch1$handedness, levels = c("left", "mostly_left", "ambidextrous", "none", "mostly_right", "right"))
bnds_psd_ch4$handedness =  factor(bnds_psd_ch4$handedness, levels = c("left", "mostly_left", "ambidextrous", "none", "mostly_right", "right"))

summary(bnds_psd_ch4)


load("~/github/muse_longitudinal/lmers/eAve_psd_med_ch1_withPAF.RData", verbose = TRUE)

peakAlpha_med_ch1 = eAve_psd_med_ch1%>%
  group_by(session_id, user_id, gender, handedness, age, age_group, sessOrder, type)%>%
  summarise(PAF = mean(PAF), 
            PAA = mean(PAA))%>%
  ungroup()%>%
  mutate(sessOrder = sessOrder - 12)
  
# no PAF or PAA in ch4

# selectCols  = c("session_id",
#   "user_id.x",
#   "gender.x",
#   "handedness.x",
#   "age.x",
#   "age_group.x",
#   "sessOrder.x" ,
#   "sessDaysSince1st.x",
#    "type" ,              "freq"   ,            "log10powM",       
#  "log10powSD" )
# 
# renameCols  = c("session_id",
#   "user_id",
#   "gender",
#   "handedness",
#   "age",
#   "age_group",
#   "sessOrder" ,
#   "sessDaysSince1st",
#    "type" ,              "freq"   ,            "log10powM",       
#  "log10powSD" )
# eAve_psd_med_ch4 = eAve_psd_med_ch4[,selectCols]
# names(eAve_psd_med_ch4) = renameCols
# peakAlpha_med_ch4 = eAve_psd_med_ch4%>%
#   group_by(session_id, user_id, gender, handedness, age, age_group, sessOrder, type)%>%
#   summarise(PAF = mode(PAF), 
#             PAA = mode(PAA))%>%
#   ungroup()%>%
#   mutate(sessOrder = sessOrder - 12)
# 
#   summary(peakAlpha_med_ch4)

```

### band ranges
+ deltaBand = c[1,4)
+ thetaBand = c[4,8)
+ alphaBand = c[8,13)
+ betaBand = c[14,30)  exluding noiseBand = c(20,23)
+ gammaBand = c[34,42)


## delta
```{r}
curBand = 'delta'

print('Left Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch1, type == "med" & freqBand == curBand))
anova(lmerObj)

print('RIGHT Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch4, type == "med" & freqBand == curBand))
anova(lmerObj)

```

## theta
```{r}
curBand = 'theta'

print('Left Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch1, type == "med" & freqBand == curBand))
anova(lmerObj)

print('RIGHT Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch4, type == "med" & freqBand == curBand))
anova(lmerObj)

```

## alpha
```{r}
curBand = 'alpha'

print('Left Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch1, type == "med" & freqBand == curBand))
anova(lmerObj)

print('RIGHT Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch4, type == "med" & freqBand == curBand))
anova(lmerObj)

```


## peak alpha frequency

```{r}

print('Left Channel')
lmerObj = lmer(PAF~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(peakAlpha_med_ch1, type == "med"))
anova(lmerObj)

```

## power at peak alpha frequency

```{r}
print('Left Channel')
lmerObj = lmer(PAA~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(peakAlpha_med_ch1, type == "med"))
anova(lmerObj)

```

## beta
```{r}
curBand = 'beta'

print('Left Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch1, type == "med" & freqBand == curBand))
anova(lmerObj)

print('RIGHT Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch4, type == "med" & freqBand == curBand))
anova(lmerObj)

```

## gamma
```{r}
curBand = 'gamma'

print('Left Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch1, type == "med" & freqBand == curBand))
anova(lmerObj)

print('RIGHT Channel')
lmerObj = lmer(log10pow_M~  age + gender + age:gender+
                sessOrder + sessOrder:age + sessOrder:gender+sessOrder:age:gender+
                  +(1|user_id), 
               data = subset(bnds_psd_ch4, type == "med" & freqBand == curBand))
anova(lmerObj)

```


